\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
notes to self

@@

>>>>

HOGG: Similarly, the spectral part of the model should also be
interpretable. HOGG SHOW FIGURE THAT DEMONSTRATES THIS, qualitatively.

@@

In that context: This model is only linear! We could have done much better with
a more flexible model. But choices, execution.

In that context: These features are bad! We could have used feature engineering
or an autoencoder to do a much better job. Definitely should do this in the future.
